---
title: "Update iAtlas Data Manifest"
date: lubridate::today()
output: html_notebook
---

```{r}
library(googlesheets)
suppressMessages(library(tidyverse))
library(feather)
```

### Download current manifest

Read current version of iAtlas manifest from shared Google Sheets URL.

```{r}
manifest_url <- "https://docs.google.com/spreadsheets/d/1DsKOfudrxW06zl__7pkbI_nLpBn9Z9cDJ40Gd6HcbFY/"
gs_auth()
manifest_gs <- gs_url(manifest_url)
```

```{r, message=FALSE}
files_gs_df <- gs_read(manifest_gs)
```

### Subset to IRWG files

```{r}
files_gs_irwg_df <- files_gs_df %>% 
    filter(isIRWG)
```

### Read latest manifest from Synapse (IRWG files)

**Note:** generated using the following command:
```
python python/data_manifest.py syn4680136 data
```

```{r}
files_syn_irwg_df <- read_feather("../data/syn4680136_manifest_2017-10-13.feather")
```

### Merge Google and Synapse based manifests (IRWG files)

```{r}
col_order <- c("isIRWG", "rootPath", "rootId", "folderPath", "folderId", 
               "entityName", "entityId", "fileName", "downloadName", 
               "externalURL", "contentMd5", "contentSize", "versionNumber", 
               "createdById", "createdByName", "createdByUser", 
               "modifiedById", "modifiedByName", "modifiedByUser",             
               "Contributor", "BigQueryTable", "FilteredAnnotatedBigQueryTable", 
               "Keep", "Phase", "Notes")
files_master_irwg_df <- files_syn_irwg_df %>% 
    left_join(files_gs_irwg_df %>% 
                  select(isIRWG, rootPath, rootId, fileId, Contributor, 
                         BigQueryTable, FilteredAnnotatedBigQueryTable,
                         Keep, Phase, Notes), 
              by = c("entityId" = "fileId")) %>% 
    rename(rootPath = rootPath.x, rootId = rootId.x) %>% 
    select(one_of(col_order)) %>% 
    replace_na(list(isIRWG = TRUE))
```

### Subset to non-IRWG files

```{r}
files_gs_other_df <- files_gs_df %>% 
    filter(!isIRWG)
```

```{r}
files_gs_other_df %>% 
    select(folderPath, folderId, entityName = fileName, entityId = fileId) %>% 
    write_feather("../data/nonIRWG_base-manifest.feather")
```

### Read latest manifest from Synapse (non-IRWG files)

```{r}
files_syn_other_df <- read_feather("../data/nonirwg_manifest_2017-10-13.feather")
```

### Merge Google and Synapse based manifests (non-IRWG files)

```{r}
col_order <- c("isIRWG", "rootPath", "rootId", "folderPath", "folderId", 
               "entityName", "entityId", "fileName", "downloadName", 
               "externalURL", "contentMd5", "contentSize", "versionNumber", 
               "createdById", "createdByName", "createdByUser", 
               "modifiedById", "modifiedByName", "modifiedByUser",             
               "Contributor", "BigQueryTable", "FilteredAnnotatedBigQueryTable", 
               "Keep", "Phase", "Notes")
files_master_other_df <- files_syn_other_df %>% 
    left_join(files_gs_other_df %>% 
                  select(isIRWG, rootPath, rootId, fileId, Contributor, 
                         BigQueryTable, FilteredAnnotatedBigQueryTable,
                         Keep, Phase, Notes), 
              by = c("entityId" = "fileId")) %>% 
    select(one_of(col_order)) %>% 
    replace_na(list(isIRWG = FALSE))
```

### Combine all files to create final manifest 

```{r}
files_master_df <- bind_rows(files_master_irwg_df, files_master_other_df)
```

### Create new worksheet and save in Google Sheets

```{r}
ws_name <- glue::glue("Files_{date}", date = lubridate::today())
manifest_gs <- manifest_gs %>% 
    gs_ws_new(ws_title = ws_name, input = files_master_df)
```

